`flippant` --- An `R` package for the automated analysis of

### 2016-07-24 inst/manuscript/manuscript.rmd
fixed x -> template_file in manuscript

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- flippant::scramblase_assay_stats(
    x, split_by_experiment = FALSE) %>%
  dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  magrittr::set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  magrittr::extract2("Experimental Series") %>%
  to_string
ppr_results_alpha_print <- ppr_results %>%
  magrittr::extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  to_string
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  flippant::scramblase_assay_traces(
    x,
    time_max_sec = 350)
  flippant::scramblase_assay_plot(
    x)
  flippant::scramblase_assay_plot(
    x,
    split_by_experiment = FALSE)
  flippant::scramblase_assay_stats(
    x,
    split_by_experiment = FALSE)
}

>>>>

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- flippant::scramblase_assay_stats(
    template_file, split_by_experiment = FALSE) %>%
  dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  magrittr::set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  magrittr::extract2("Experimental Series") %>%
  to_string
ppr_results_alpha_print <- ppr_results %>%
  magrittr::extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  to_string
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  flippant::scramblase_assay_traces(
    template_file,
    time_max_sec = 350)
  flippant::scramblase_assay_plot(
    template_file)
  flippant::scramblase_assay_plot(
    template_file,
    split_by_experiment = FALSE)
  flippant::scramblase_assay_stats(
    template_file,
    split_by_experiment = FALSE)
}
